Parallel Adaptive Importance Sampling

### 2016-12-04 PAIS.tex
Made it clear that we save (w,Y) as the sample not X.

The proposal distribution could be constructed in many different ways,
but we choose to use a mixture distribution, made up of a sum of MCMC
proposal distributions for each of the members of the ensemble. Once the proposal is
constructed, we can sample a new set of states from the proposal
distribution, and each is assigned a weight given by the ratio of the target
density and the proposal mixture distribution density. Assuming that
our proposal distribution is a good one, then the variance of the
weights will be small, and we will have many useful samples. Finally, we
need to create a set of evenly weighted samples which best represent
this set of weighted samples. This is achieved by implementing a
resampling algorithm. Initially we will use the
ETPF algorithm\cite{reich2013nonparametric}, although we will suggest an alternative strategy in
Section \ref{sec:AMR}. The output of the resampling algorithm gives us
a set of evenly weighted
samples that we believe represents the target distribution well, and
from this point we
can iterate the process once again. The algorithm is summarised in Algorithm \ref{alg:PAIS}.

@@

		Resample: $(\W^{(i)},\Y^{(i)}) \rightarrow (\frac{1}{M}\mathbf{1}, \X^{(i)})$.
	}
\caption{The parallel adaptive importance sampler (PAIS).\label{alg:PAIS}}
\end{algorithm}
\end{table}

@@

The key is to choose a suitable transition kernel $\nu$ such that
if $X^{(i)}$ is a good representative sample of the posterior,
then the mixture density $\chi(\cdot;\X^{(i)})$ is a good
approximation of the posterior distribution. If this is the case,
the newly proposed states $\Y^{(i)}$ will also be a good sample of the posterior with low variance in the
weights $\W^{(i)}$.

>>>>

The proposal distribution could be constructed in many different ways,
but we choose to use a mixture distribution, made up of a sum of MCMC
proposal distributions for each of the members of the ensemble. Once the proposal is
constructed, we can sample a new set of states from the proposal
distribution, and each is assigned a weight given by the ratio of the target
density and the proposal mixture distribution density. Assuming that
our proposal distribution is a good one, then the variance of the
weights will be small, and we will have many useful samples. Finally, we
need to create a set of evenly weighted samples which best represent
this set of weighted samples. This is achieved by implementing a
resampling algorithm. Initially we will use the ETPF
algorithm\cite{reich2013nonparametric}, although we will suggest an
alternative strategy in Section \ref{sec:AMR}. The resampling
algorithm gives us a set of evenly weighted samples which represents
the target distribution well, which we can use to iterate the process
again. The algorithm is summarised in Algorithm \ref{alg:PAIS}.

@@

		Resample: $(\W^{(i)},\Y^{(i)}) \rightarrow (\frac{1}{M}\mathbf{1}, \X^{(i)})$.
	}
	Output $(\W, \Y)$.\;
\caption{The parallel adaptive importance sampler (PAIS).\label{alg:PAIS}}
\end{algorithm}
\end{table}

@@

The key is to choose a suitable transition kernel $\nu$ such that
if $X^{(i)}$ is a representative sample of the posterior,
then the mixture density $\chi(\cdot;\X^{(i)})$ is a good
approximation of the posterior distribution. If this is the case,
the newly proposed states $\Y^{(i)}$ will also be a good sample of the posterior with low variance in the
weights $\W^{(i)}$.
